MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
new tries - hot hand theory

player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}
player_and_game(202681, 21400681)

@@

list_per_player <- list()
j <- 1
for(i in ourtable$player_id) {
   streak_per_player[[j]] <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   j <- j + 1
}
streak_per_player

>>>>

#Create a function that gives us a vector of streaks for a specific player and game
player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}
player_and_game(202681, 21400681)

@@

#Create a list that gives us the streaks of each player and game (10 best performances)
streak_per_player <- list()
j <- 1
for(i in ourtable$player_id) {
   streak_per_player[[j]] <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   j <- j + 1
}
streak_per_player

#Create a data frame for the strikes of each one of the 10 players (cannot create a data.frame including all of them, because each list has different length)
player1_df <- data.frame('streaks' = streak_per_player[[1]])
player2_df <- data.frame('streaks' = streak_per_player[[2]])
player3_df <- data.frame('streaks' = streak_per_player[[3]])
player4_df <- data.frame('streaks' = streak_per_player[[4]])
player5_df <- data.frame('streaks' = streak_per_player[[5]])
player6_df <- data.frame('streaks' = streak_per_player[[6]])
player7_df <- data.frame('streaks' = streak_per_player[[7]])
player8_df <- data.frame('streaks' = streak_per_player[[8]])
player9_df <- data.frame('streaks' = streak_per_player[[9]])
player10_df <- data.frame('streaks' = streak_per_player[[10]])
ourtable

#Visualisation for 10 players
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = 'Kyrie Irving')
